On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-05-15 main.tex
typos

Throughout this section, $f$ and $i \in \{1,\hdots,n\}$ are fixed. We
prove that there exists a hypersurface $\D_{i} \subset \C^{n\times
  n}$ of degree at most $5n^2(2d)^{2n}$ such that if $\mA$ is not in $\D_{i}$,
then $\mA$ is invertible and satisfies both conditions in
$\textbf{H}_i$.

>>>>

Throughout this section, $f$ and $i \in \{1,\hdots,n\}$ are fixed. We
prove that there exists a non-zero polynomial $\D_{i}$ in $n^2$
variables and of degree at most $5n^2(2d)^{2n}$ such that if $\mA$ does
not cancel $\D_{i}$, then $\mA$ is invertible and satisfies both
conditions in $\textbf{H}_i$.
